### 2019-03-08 paper/sex_selection_spacing-ver2.tex
Show 25, 50, and 75 percentiles spacing in one graph
This also introduces \mcth to cover multicolumn{3}{c}{} in LaTeX
Remove reference to non-existing paper

% \bibpunct{(}{)}{;}{a}{}{,}
\newcommand{\mco}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\mct}[1]{\multicolumn{2}{c}{#1}}
\newcommand{\X}{$\times$ }
\newcommand{\hs}{\hspace{15pt}}

@@

Both of the last two results are different from prior studies using NFHS data.
There are two potential explanations.
First, the NFHS-4 is substantially larger than the three prior surveys.
Hence, it is possible that the effects have been there all along, but 
we did not have the power to detect them.
Second, it is possible that at least the first-born results are an
artifact of any recall error not captured by the data restrictions.
Certain types of recall error would also explain why the sex ratio for
the second spell and one boy is statistically significantly \emph{below} 
the natural sex ratio \citep{Portner2018b}.

>>>>

% \bibpunct{(}{)}{;}{a}{}{,}
\newcommand{\mco}[1]{\multicolumn{1}{c}{#1}}
\newcommand{\mct}[1]{\multicolumn{2}{c}{#1}}
\newcommand{\mcth}[1]{\multicolumn{3}{c}{#1}}
\newcommand{\X}{$\times$ }
\newcommand{\hs}{\hspace{15pt}}

@@

Both of the last two results are different from prior studies using NFHS data.
There are two potential explanations.
First, the NFHS-4 is substantially larger than the three prior surveys.
Hence, it is possible that the effects have been there all along, but 
we did not have the power to detect them.
Second, it is possible that at least the first-born results are an
artifact of any recall error not captured by the data restrictions.
Certain types of recall error would also explain why the sex ratio for
the second spell and one boy is statistically significantly \emph{below} 
the natural sex ratio.
